---
title: "Package viser"
author: "Obaid Ur Rehman,Muhammad Habib"
date: "October 2, 2018"
output:
  prettydoc::html_pretty:
    theme: cayman
    highlight: github
  html_document:
    toc: true
    toc_depth: 2
vignette: >
  %\VignetteIndexEntry{viser}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r iris, include=FALSE}
library(viser)
```

## Introduction
This package uses data.motogomery API to get and analayse crimme data for mmontgomery county.

The package contains the following functionalities:

* #### getLimitedData(limit = 500):
  Fetches the crime data limited by variable limit as function argument.
    + Example:
        ``` {r data,message=FALSE, warning=FALSE}
        data <- getLimitedData(limit = 500)
        head(data)
        ```
* #### getDataByCrimeType(dataset, crimetype):
  The print function displays coefficients along with their names
    + Example:
        ``` {r crimedata,message=FALSE, warning=FALSE}
        data <- getDataByCrimeType(data, 2)
        head(data)
        ``` 
* #### getCrimeByID(id):
  Returns the crime type.
      > Example:
          ``` {r crimeid, echo=FALSE,message=FALSE, warning=FALSE}
          crime <- getCrimeByID(2)
          print(crime)
          ```
          
* #### Note:

  Unable to eradicate below warning:
  
    checking R code for possible problems ... NOTE
    cleanData: no visible binding for global variable ‘crimename3’
    Undefined global functions or variables:
      crimename3
      
    Eventhough, crimename3 is a column in dataframe.
